Efficiency

### 2018-01-02 DraftExec.Rnw
little fixes in bib etc. Still needs some work

The paper makes no effort to justify the selection of choice of jets on the efficiency of the propulsion system, instead focussing on improved acoustic performance, and potential machinery space-saving advantages.  The the vessel under consideration would require 250 tonnes more fuel with jets find than with propellers, the jets would require more power to reach equal waterspeed to a conventionally propelled craft right up to 30 kt. The paper states: "This is an encouraging result for a first iteration as the AWJ-21™ arrangement has not been fully optimised and, hence, there is further prospect of reducing the shaft power for this form. If the power could be reduced by 5\% (e.g. by fur ther improving the waterjet/hull fairing), then the AWJ-21™ vessel would be better at all speeds above 25 knots." \parencite{giles2010}

@@

Moreover, recent literature seems to confirm that efficiency of pumpjets fall off precipitously towards zero the closer that the vessel speed comes to zero.  This stronly suggests the existence of some fundamental constraint in the physics of the operation of jets, which recent advances in technology seems not to have overcome.  To more firmly establish the extent to which adaptation or plausible improvments in technology could or could not change this trend, it is worthwhile considering the theoretical limits that are presented by the physics.  This should further limit the range of error that might be made in estimating realistic bounds of performance for an unknown system.

@@

With the optimum efficiency of a jet probably being no greater than 60\% or 70\% at its peak efficiency according to many theoretical and experimental studies \parencite{lu2015}, which would quite probably lie considerably higher in terms of waterspeed, these facts, along with the inevitable decline of efficiency towards zero as waterspeed also declines, a suitably constrained set of plausible efficiency curves may be investigated numerically, as will be done later in later sections.

@@

\begin{figure}
\includegraphics[width=\textwidth]{DuctedEfficiency.png}
\caption{Calculations of 'ideal' efficiencies of accelerating ducts (neglecting drag) in \cite{oosterveld1970} show that a duct can only improve the efficiency of a propeller if it is loaded above a certain degree, and that longer ducts produce better improvements in 'ideal' efficiencies}
\label{fig:DuctedEfficiency.png}
\end{figure}

@@

However, when dived, it might be reasonably assumed that the complete elimination of all sources of cavitition will be the primary objective of acoustic signature management.  This is neatly put in \cite[88]{gearhart1966}: "The occurence of cavitation in a propulsor results in adegradation of the propulsor operating characteristics if extensive amounts of cavitation exist, and in significant noise when minute amounts occur.  As a result, the performance requirements of a submersible weapon system specify that the occurence or inception of cavitation be avoided below certain operating depths." One might consider that a submarines 'tactical silent speed' would most probably correspond to the speed at which it can operate safely below the point of any cavitation inception.

>>>>

The paper makes no effort to justify the selection of choice of jets on the efficiency of the propulsion system, instead focussing on improved acoustic performance, and potential machinery space-saving advantages.  The vessel under consideration would require 250 tonnes more fuel with jets find than with propellers, the jets would require more power to reach equal waterspeed to a conventionally propelled craft right up to 30 kt. The paper states: "This is an encouraging result for a first iteration as the AWJ-21™ arrangement has not been fully optimised and, hence, there is further prospect of reducing the shaft power for this form. If the power could be reduced by 5\% (e.g. by fur ther improving the waterjet/hull fairing), then the AWJ-21™ vessel would be better at all speeds above 25 knots." \parencite{giles2010}

@@

Moreover, recent literature seems to confirm that efficiency of pumpjets fall off precipitously towards zero the closer that the vessel speed comes to zero.  This strongly suggests the existence of some fundamental constraint in the physics of the operation of jets, which recent advances in technology seems not to have overcome.  To more firmly establish the extent to which adaptation or plausible improvments in technology could or could not change this trend, it is worthwhile considering the theoretical limits that are presented by the physics.  This should further limit the range of error that might be made in estimating realistic bounds of performance for an unknown system.

@@

With the optimum efficiency of a jet probably being no greater than 60\% or 70\% at its peak efficiency according to many theoretical and experimental studies \parencite{lu2016cfd}, which would quite probably lie considerably higher in terms of waterspeed, these facts, along with the inevitable decline of efficiency towards zero as waterspeed also declines, a suitably constrained set of plausible efficiency curves may be investigated numerically, as will be done later in later sections.

@@

\begin{figure}
\includegraphics[width=\textwidth]{AcceleratingIdeal.png}
\caption{Calculations of 'ideal' efficiencies of accelerating ducts (neglecting drag) in \cite{oosterveld1970} show that a duct can only improve the efficiency of a propeller if it is loaded above a certain degree, and that longer ducts produce better improvements in 'ideal' efficiencies}
\label{fig:AcceleratingIdeal.png}
\end{figure}

@@

However, when dived, it might be reasonably assumed that the complete elimination of all sources of cavitition will be the primary objective of acoustic signature management.  This is neatly put in \cite[88]{gearhart1966selection}: "The occurence of cavitation in a propulsor results in adegradation of the propulsor operating characteristics if extensive amounts of cavitation exist, and in significant noise when minute amounts occur.  As a result, the performance requirements of a submersible weapon system specify that the occurence or inception of cavitation be avoided below certain operating depths." One might consider that a submarines 'tactical silent speed' would most probably correspond to the speed at which it can operate safely below the point of any cavitation inception.

### 2018-01-02 DraftExec.tex
add plots
little fixes in bib etc. Still needs some work

>>>>

\section{App Outputs}

Adjustable figures from App.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# in df}}\begin{verbatim}
## # A tibble: 6 x 4
##     kts   eff.jet  eff.prop hotel
##   <dbl>     <dbl>     <dbl> <dbl>
## 1   0.5 0.1728660 0.8902062   150
## 2   1.0 0.2052115 0.8669509   150
## 3   1.5 0.2356997 0.8463204   150
## 4   2.0 0.2643992 0.8277603   150
## 5   2.5 0.2913788 0.8108753   150
## 6   3.0 0.3167071 0.7953734   150
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# speed.}}\begin{verbatim}
## [1] 2.5
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# power.}}\begin{verbatim}
## [1] 150
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# df.}}\begin{verbatim}
## # A tibble: 6 x 3
##     kts hotel       eff
##   <dbl> <dbl>     <dbl>
## 1   0.5   150 0.1728660
## 2   1.0   150 0.2052115
## 3   1.5   150 0.2356997
## 4   2.0   150 0.2643992
## 5   2.5   150 0.2913788
## 6   3.0   150 0.3167071
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# index.}}\begin{verbatim}
## [1] 5
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# eff.}}\begin{verbatim}
##         5 
## 0.2913788
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# const is 2.8}}\end{kframe}
\end{knitrout}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figures/plots-plot_eff-1}

}

\end{knitrout}
\caption{Efficiency}
\label{fig:Efficiency_plot}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figures/plots-plot_end-1}

}

\end{knitrout}
\caption{Endurance}
\label{fig:Endurance_plot}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figures/plots-plot_range-1}

}

\end{knitrout}
\caption{Range}
\label{fig:Range_plot}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figures/plots-plot_power-1}

}

\end{knitrout}
\caption{Power}
\label{fig:Power_plot}
\end{figure}
